---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
<!-- To generate README.md with following commands: -->
```{r, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
library(pipeR)
knitr::knit(input="README.rmd", output = "README.md")
readLines("README.md") %>>% `[`(12:length(.)) %>>% write("README.md")
```


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Status

     License       |  Linux/osx Build  |   Windows Build   |  Coverage Status  |        CRAN       |
-------------------|-------------------|-------------------|-------------------|-------------------|
[![GitHub license](https://img.shields.io/badge/lincense-MIT-blue.svg)](http://badges.mit-license.org) | [![Build status](https://travis-ci.org/ChingChuan-Chen/rfda.svg?branch=master)](https://travis-ci.org/ChingChuan-Chen/rfda/branches) | [![Build status](https://ci.appveyor.com/api/projects/status/2yms6ao3mf69fdht/branch/master?svg=true)](https://ci.appveyor.com/project/ChingChuan-Chen/rfda/branch/master) | [![Coverage Status](https://codecov.io/github/ChingChuan-Chen/rfda/coverage.svg?branch=master)](https://codecov.io/github/ChingChuan-Chen/rfda?branch=master) | [![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/rfda)](http://cran.r-project.org/package=rfda)   [![Downloads](http://cranlogs.r-pkg.org/badges/grand-total/rfda)](http://cran.rstudio.com/package=rfda)

# rfda

To provide some tools used in functional data analysis.

## Installation

You can install:

* the latest development version from github with

    ```R
    install.packages("devtools")
    devtools::install_github("ChingChuan-Chen/rfda")
    ```

If you encounter a bug, please file a reproducible example on [github](https://github.com/ChingChuan-Chen/rfda/issues).

## examples

To be done.
